Syntactic realization with data-driven neural tree grammars

### 2016-10-11 paper/draft.tex
jk. submitting this version. license implanted

@@

From this input, we extracted the atomic supertag prediction instances
and trained a network defined by each of the architectures of
\ref{sec:models} and each of the supertag representations of
\ref{sec:neural}.  As always, we used Section 02-21 for development,
Sections 22 for training, and Section 23 for testing.  A complete
description of network organization and training parameters is given
in the appendix.  The code and complete experimental setup are publically available\footnote{https://github.com/braingineer/neural\_tree\_grammar}.

@@

In this appendix, we describe some design decisions that took place which did not have a place in the paper but should still be reported.  In particular, this section covers the data processing, parameters used in the final model, and design decisions for the restricting the supertag distributions. As a reminder, the code, tex sources, and experimental setup are hosted on github\footnote{https://github.com/braingineer/neural\_tree\_grammar}.

>>>>

\blfootnote{
    % % final paper: en-us version (to licence, a license)
    %
    \hspace{-0.65cm}  % space normally used by the marker
    This work is licenced under a Creative Commons 
    Attribution 4.0 International License.
    License details:
    \url{http://creativecommons.org/licenses/by/4.0/}
}

@@

From this input, we extracted the atomic supertag prediction instances
and trained a network defined by each of the architectures of
\ref{sec:models} and each of the supertag representations of
\ref{sec:neural}.  As always, we used Section 02-21 for development,
Sections 22 for training, and Section 23 for testing.  A complete
description of network organization and training parameters is given
in the appendix.  The code and complete experimental setup are publically available\footnote{\url{https://github.com/braingineer/neural_tree_grammar}}.

@@

In this appendix, we describe some design decisions that took place which did not have a place in the paper but should still be reported.  In particular, this section covers the data processing, parameters used in the final model, and design decisions for the restricting the supertag distributions. As a reminder, the code, tex sources, and experimental setup are hosted on github\footnote{\url{https://github.com/braingineer/neural_tree_grammar}}.
